Starcode: an exact algorithm for sequence clustering

### 2014-07-03 doc/document.tex
Updated the manuscript. Added a figure.

\begin{methods}
\section{Methods}
\subsection{Inexact string matching using tries}
The matching method of starcode is based on a variation of the Needleman-Wunsch
(NW) algorithm \citep{pmid5420325}. In the original algorithm
(Figure~\ref{fig:01}a), the Levenshtein distance between two sequences is found
by applying a recurrence relation throughout a matrix of $mn$ terms, where $m$
and $n$ are the respective sequence lengths. The complexity of this dynamic
programming approach is $O(mn)$.

\begin{figure}[!tpb]%figure1
\centerline{\includegraphics{Fig1.pdf}}
\caption{Needleman-Wunsch (NW) alignment. \textbf{a}
  Alignment of GTTGCA and GATCCA using
the NW alignment matrix. The margins (purple) are initialized and the cells of
the matrix (yellow) are computed from left to right and from top to bottom by
the following
dynamic programming algorithm. The value in each cell is computed from the values
of the neighboring top, left and top-left cells. Denoting $a$, $b$ and $c$ these
respective terms, the value in the cell of coordinates $(i,j)$ is computed as
$\min(a+1, b+1, c)$ if the $i$-th letter from the first sequence is identical to
the $j$-th letter from the second, or $\min(a+1, b+1, c+1)$ if the letters are
different. The Levenshtein distance
between the two sequences is found in the bottom right cell. \textbf{b}
Lower complexity algorithm to
determine whether GTTGCA and GATCCA are 2-neighbors. The values in purple cells
are set during initialization. The dynamic programming algorithm proceeds as above,
with the difference that it is interrupted if the value of a diagonal cell (bold
borders) is larger than 2. The values in purple cells are not always the same as
their equivalent in a (purple arrow), but the values in the yellow cells are
nevertheless identical. The values of the white cells are never computed, which
contributes to making the algorithm less complex.}\label{fig:01}
\end{figure}

In many instances, the only information of interest is to find out whether the
sequences are $d$-neighbors (separated by a distance less than or equal to a
threshold $d$).  In that case, the complexity then reduces to
$O(d \min(m,n))$ as described below \citep{ukkonen}. Instead
of initializing the margins of the matrix and computing all the
terms, the matrix is initialized as shown on Figure~\ref{fig:01}b and only the
terms around
the diagonal are computed. If the computation of a diagonal term yields a value
greater than $d$, the distance is known to be greater than $d$ and the process
is halted. Otherwise, the bottom-right term indicates the actual distance
between the sequences, as in the NW algorithm.

This method can be used for inexact matching of sequences against a reference
set indexed as prefix tree, also known as a trie \citep{ukkonen}. The terms of the
matrix are updated row-wise as a depth-first search traverses the trie from the
root, as illustrated in Figure~\ref{fig:02}. Every time a node is visited, the row
corresponding to its depth is recomputed. If the threshold value $d$ is exceeded
for a diagonal term, the Levenshtein distance for all the downstream sequences is
also necessarily greater than $d$. Therefore, no more hits are to be discovered
in this path and the depth-first search backtracks to the parent node. When the
process halts, every tail node
(corresponding to a sequence of the database) on the path of this search is a
$d$-neighbor of the query. This method is efficient because it eliminates large
areas of the search space, and because the NW alignment of the query with each
prefix of the database is computed only once.

\begin{figure}[!tpb]%figure2
\centerline{\includegraphics{Fig2.pdf}}
\caption{Trie query with NW alignment. Each sequence of the index is a path in
the trie. The query GTTGCA is written at the top of a NW matrix, which is
initialized as shown on Figure~\ref{fig:01}b. The trie is traversed by a
depth-first search (red path) from the root. At each depth, the node added to
the path is written on the left of the NW matrix and the row is computed.
Checkpoints from 1 to 4 (circled red numbers) show the state of the NW matrix
as the search proceeds. The node labelled 3 is a leaf and thus corresponds to a
2-neighbor of the query. The search path then backtracks to the node labelled 2
and the last rows of the NW are erased. The search path then goes to node labelled
4, in which case the newly computed diagonal cell exceeds the threshold (circled
in red). Even if this node has children, they are not visited (red crosses).}
\label{fig:02}
\end{figure}

@@

However, storing the rows of the NW matrix in the nodes, as suggested by the
approach described in the previous section is not optimal. At depth equal to the
length of the shared prefix, say $k$, the terms on the right of the diagonal were
computed using characters that belong to the previous query. Since they also depend
on the terms computed at lower depth, the search cannot restart at depth $k$. This
issue is solved by storing in each node a combination of row and column terms that
form an angle shape, looking
like a horizontally flipped L character as shown on Figure~\ref{fig:03}. This way, the
computation intermediates stored in a node of depth $k$ depend only on the previous
characters of the query. Using this technique, the search can effectively restart
at a depth equal to the length of the shared prefix with the previous query, thereby
averting the need to recompute the first terms of the NW alignments.

@@

\begin{figure}[!tpb]%figure3
\centerline{\includegraphics{Fig3.pdf}}
\caption{Poucet search algorithm. The algorithm proceeds with the same principles
as shown on Figure~\ref{fig:02} with the difference that the NW matrix is not
updated row-wise, but along horizontally flipped L shapes. As the depth-first
search proceeds, these values are stored in the nodes of the trie. Only the nodes
at the top contain initialized values; for the other nodes, the values at the
border are implicitly known to be 3. Since the values in the vertical part of
the flipped L are the same for every child of the same node, they are computed
only once (purple arrow). The values in the grey cells will be computed as the
search path (red) visits the node. Storing the intermediates in the nodes allows
the next query to restart at depth $k$ if it shares a common prefix of length
$k$ with the current query.}
\label{fig:03}
\end{figure}

\subsection{Lookup search}
If the Levenshtein distance between two sequences of length $L$ is
less then or equal to $\tau$, then there must exist a perfect
match of length at least $k = L / (\tau+1)$, assuming for the time being
that $k$ is an integer.
We take advantage of this property to build a lookup table containing
all such $k$-mers from sequences inserted in the trie. When
a new sequence is queried, subsequences are first extracted from it
and queried against the lookup table. If none of the subsequences
are found, the minimum distance between the query and all the
sequences in the trie is at least $\tau+1$, and the trie-search can
therefore be omitted. This lookup is particulary useful for long query
sequences because in this case $k$ is large. The probability of an
exact match between subsequences of length $k$ is small and the
trie-search will be avoided for many such queries. The absence of match
is detected at the computational cost of several table lookups, compared
to the higher cost of measuring the Levenshtein distance between long
sequences.

@@

\subsection{Seek and construct}
To reduce the size of the search space, we use a dynamic ``seek and construct''
approach whereby queries are processed meanwhile the trie is built. In other
words, each sequence is matched against the trie before it is inserted. To
illustrate why the trie does not need to contain all the sequences upon query,
assume that two sequences A and B are $d$-neighbors. A is processed first. Since
B is not yet inserted, A yields no hit. It is then inserted in the trie. At the
time B is processed, A is a hit for the query and the match A-B is discovered.
This approach guarantees that every hit is discovered, while maintaining the
trie as ``thin'' as possible, thereby reducing the search time.
%The whole matching process is summarized in the pseudocode shown Figure~\ref{fig:04}
The whole matching process is summarized in the pseudocode shown in
Algorithms~\ref{alg:starcode} and \ref{alg:poucet}.

@@

\section{Results}
\subsection{Benchmark against sequence clustering algorithms}
Sequence clustering is routinely used to curate databases of non
redundant nucleotide or protein sequences. We benchmarked starcode
against the two popular sequence clustering algorithms CD-HIT
\citep{pmid23060610} and USEARCH \citep{pmid20709691}.

@@

Using 12 cores, starcode clustered the shuffled 50 million sequences
in 4 minutes and 32 seconds without a single error (the output
consisted of 1 million clusters of size 50).  The running times
of CD-HIT and USEARCH were [59] and [64] minutes respectively, and they
identified 2,362,352 and 2,739,954 clusters respectively. The results
are summarized in Figure~\ref{fig:04}. Both algorithms rely on
heuristics, explaining why the number of clusters is off target. These
results clearly demonstrate that starcode outperforms other clustering
algorithms in speed and accuracy to cluster random sequences.

@@

\begin{figure}[!tpb]%figure5
\centerline{\includegraphics{Fig4.pdf}}
\caption{Benchmark of starcode against sequence clustering algorithms
and short read mappers. \textbf{a} Running time compared to CD-HIT and
UCLUST on the dataset described in the text. \textbf{b} Error rate
compared to CD-HIT and UCLUST, expressed as the percentage of clusters
failing to be merged. \textbf{c} Running time compared to Bowtie2, BWA
and GEM on this dataset. The running time is decomposed in extraction
of unique sequences (purple), Burrows-Wheeler indexing (yellow), and
query proper (white). The extraction was performed with the Linux sort
command, so the time is the same in every case. \textbf{d} Error rate
compared to Bowtie2, BWA and GEM, expressed as the proportion of matches
with a single hit. This is an underestimate of the true error rate.}
\label{fig:04}
\end{figure}

@@

For this test, we used the same dataset described above, in which every
sequence has at least 2 distinct matches at a distance 3 (mutant sequences
from the same cluster may be at a distance up to 6). This means that we
can use matches with a single hit (themselves) as a lower bound on the inaccuracy.
We used unique sequences to build an index and queried the index with the same
sequences. Figure~\ref{fig:04}c shows the running time of starcode along with the
decomposition of the running time for the three mappers. Note that the time to
extract unique sequences is always the same because we used the Linux
\texttt{sort -u} command in every case. It appears that the running time of
starcode is about the same as the time required by BWA (the fastest aligner in
this test) to index and run the query proper. Figure~\ref{fig:04}d shows the
lower bound on
the error rate, as estimated by the proportion of single hits. BWA was found to
be the most accurate aligner with a lower bound of 19\% errors. This measure
is indeed an underestimate of the true error rate, but given that starcode makes no
mistake on this dataset, a more accurate measure is not necessary. In conclusion,
starcode runs slightly faster than short read mappers when all steps are taken
into account, and clearly outperforms them in precision on this particular problem.

@@

We set up a test based on the meningitis-causing agent
\textit{Neisseria meningitidis}. The genome of this bacterium is interspersed
with a frequent 12 bp sequence known as DNA uptake sequence \citep{pmid10673000}. We
extracted the 12-mers from both orientations of  the 2.19 Mb genome, yielding
4.39 million 12-mers, consisting of 2.77 million unique sequences. Clustering
the 12-mers with starcode within a Levenshtein distance of 2 took less
than 3 minutes with 20 cores. We identified the known DNA uptake sequence of
\textit{Neisseria meningitidis} (ATGCCGTCTGAA) as the most abundant 12-mer, comprising
1,466 exact matches and 4,625 inexact matches. This result testifies to the
fact that starcode can be used to identify biologically relevant motifs in
bacterial genomes.

To test starcode on the scale of a metazoan genome, we used a \textit{Drosophila}
dataset from \cite{pmid20888037}. The study describes two
signatures of chromatin proteins called Red and Yellow, both corresponding
to transcribed regions of the genome. The distinction is based on epigenomic
features only, which prompted us to identify sequence features that could
discriminate Red \textit{versus} Yellow regions. To this end, we used starcode to
cluster 18-mers from both regions.

The total coverage of Red and Yellow chromatin in the \textit{Drosophila} genome is
10.7 Mb and 21.3 Mb respectively, corresponding to 21.5 million and 42.5 million
18-mers, respectively. We used starcode to identify clusters of 18-mers within
a Levenshtein distance of 3 (the running time was approximately 35 minutes for
Red and 70 minutes for Yellow chromatin using 20 threads). The most discriminating
18-mer was (GA)$_9$, which showed a 4.8 fold enrichment in Red \textit{versus} Yellow
chromatin.
We counted 832 exact matches and 6,749 inexact matches over 3,880 distinct
18-mers in Red chromatin, showing that a larger portion of the signal comes
from inexact matches. Taken together, these results show that starcode can be
used to cluster short k-mers from metazoan-scale datasets.

@@

The speed of starcode also makes it proficient at more general clustering
problems, such as identifying enriched k-mers in genomes and in experimental
data. Here we have given two examples of such applications. In the first, we
recover a known enriched 12-mer in the genome of \textit{Neisseria meningitidis}.
In the second, we identify a sequence feature that discriminates genomic
regions found in two different chromatin types in \textit{Drosophila}. GA
repeats are known to be bound \textit{in vivo} by the protein GAF
\citep{pmid12601174}, which suggests
that this transcription factor is instrumental in setting the distinction
between Red and Yellow chromatin.

>>>>

\begin{methods}
\section{Methods}
\subsection{Inexact string matching using tries}
The matching method of starcode is based on a variation of the Needleman-Wunsch
(NW) algorithm \citep{pmid5420325}. In the original algorithm
(Figure~\ref{fig:NW}a), the Levenshtein distance between two sequences is found
by applying a recurrence relation throughout a matrix of $mn$ terms, where $m$
and $n$ are the respective sequence lengths. The complexity of this dynamic
programming approach is $O(mn)$.

\begin{figure}[!tpb]
\centerline{\includegraphics{NW.pdf}}
\caption{Needleman-Wunsch (NW) alignment. \textbf{a}
  Alignment of GTTGCA and GATCCA using
the NW alignment matrix. The margins (purple) are initialized and the cells of
the matrix (yellow) are computed from left to right and from top to bottom by
the following
dynamic programming algorithm. The value in each cell is computed from the values
of the neighboring top, left and top-left cells. Denoting $a$, $b$ and $c$ these
respective terms, the value in the cell of coordinates $(i,j)$ is computed as
$\min(a+1, b+1, c)$ if the $i$-th letter from the first sequence is identical to
the $j$-th letter from the second, or $\min(a+1, b+1, c+1)$ if the letters are
different. The Levenshtein distance
between the two sequences is found in the bottom right cell. \textbf{b}
Lower complexity algorithm to
determine whether GTTGCA and GATCCA are 2-neighbors. The values in purple cells
are set during initialization. The dynamic programming algorithm proceeds as above,
with the difference that it is interrupted if the value of a diagonal cell (bold
borders) is larger than 2. The values in purple cells are not always the same as
their equivalent in a (purple arrow), but the values in the yellow cells are
nevertheless identical. The values of the white cells are never computed, which
contributes to making the algorithm less complex.}\label{fig:NW}
\end{figure}

In many instances, the only information of interest is to find out whether the
sequences are $d$-neighbors (separated by a distance less than or equal to a
threshold $d$).  In that case, the complexity then reduces to
$O(d \min(m,n))$ as described below \citep{ukkonen}. Instead
of initializing the margins of the matrix and computing all the
terms, the matrix is initialized as shown on Figure~\ref{fig:NW}b and only the
terms around
the diagonal are computed. If the computation of a diagonal term yields a value
greater than $d$, the distance is known to be greater than $d$ and the process
is halted. Otherwise, the bottom-right term indicates the actual distance
between the sequences, as in the NW algorithm.

This method can be used for inexact matching of sequences against a reference
set indexed as prefix tree, also known as a trie \citep{ukkonen}. The terms of the
matrix are updated row-wise as a depth-first search traverses the trie from the
root, as illustrated in Figure~\ref{fig:trie}. Every time a node is visited, the row
corresponding to its depth is recomputed. If the threshold value $d$ is exceeded
for a diagonal term, the Levenshtein distance for all the downstream sequences is
also necessarily greater than $d$. Therefore, no more hits are to be discovered
in this path and the depth-first search backtracks to the parent node. When the
process halts, every tail node
(corresponding to a sequence of the database) on the path of this search is a
$d$-neighbor of the query. This method is efficient because it eliminates large
areas of the search space, and because the NW alignment of the query with each
prefix of the database is computed only once.

\begin{figure}[!tpb]
\centerline{\includegraphics{trie.pdf}}
\caption{Trie query with NW alignment. Each sequence of the index is a path in
the trie. The query GTTGCA is written at the top of a NW matrix, which is
initialized as shown on Figure~\ref{fig:NW}b. The trie is traversed by a
depth-first search (red path) from the root. At each depth, the node added to
the path is written on the left of the NW matrix and the row is computed.
Checkpoints from 1 to 4 (circled red numbers) show the state of the NW matrix
as the search proceeds. The node labelled 3 is a leaf and thus corresponds to a
2-neighbor of the query. The search path then backtracks to the node labelled 2
and the last rows of the NW are erased. The search path then goes to node labelled
4, in which case the newly computed diagonal cell exceeds the threshold (circled
in red). Even if this node has children, they are not visited (red crosses).}
\label{fig:trie}
\end{figure}

@@

However, storing the rows of the NW matrix in the nodes, as suggested by the
approach described in the previous section is not optimal. At depth equal to the
length of the shared prefix, say $k$, the terms on the right of the diagonal were
computed using characters that belong to the previous query. Since they also depend
on the terms computed at lower depth, the search cannot restart at depth $k$. This
issue is solved by storing in each node a combination of row and column terms that
form an angle shape, looking
like a horizontally flipped L character as shown on Figure~\ref{fig:poucet}. This way, the
computation intermediates stored in a node of depth $k$ depend only on the previous
characters of the query. Using this technique, the search can effectively restart
at a depth equal to the length of the shared prefix with the previous query, thereby
averting the need to recompute the first terms of the NW alignments.

@@

\begin{figure}[!tpb]
\centerline{\includegraphics{poucet.pdf}}
\caption{Poucet search algorithm. The algorithm proceeds with the same principles
as shown on Figure~\ref{fig:trie} with the difference that the NW matrix is not
updated row-wise, but along horizontally flipped L shapes. As the depth-first
search proceeds, these values are stored in the nodes of the trie. Only the nodes
at the top contain initialized values; for the other nodes, the values at the
border are implicitly known to be 3. Since the values in the vertical part of
the flipped L are the same for every child of the same node, they are computed
only once (purple arrow). The values in the grey cells will be computed as the
search path (red) visits the node. Storing the intermediates in the nodes allows
the next query to restart at depth $k$ if it shares a common prefix of length
$k$ with the current query.}
\label{fig:poucet}
\end{figure}

\subsection{Lookup search}
If the Levenshtein distance between two sequences of length $L$ is
less then or equal to $\tau$, then there must exist a perfect
match of length at least $k = L / (\tau+1)$, assuming for the time being
that $k$ is an integer.
We take advantage of this property to build a lookup table containing
all such $k$-mers from sequences inserted in the trie. When
a new sequence is queried, subsequences are first extracted from it
and queried against the lookup table. If none of the subsequences
are found, the minimum distance between the query and all the
sequences in the trie is at least $\tau+1$, and the trie search can
therefore be omitted. This lookup is particulary useful for long query
sequences (see \ref{scalability}). In this case $k$ is large, so the
probability of an exact match between subsequences of length $k$ is small.
The absence of match is detected at the computational cost of several
table lookups, compared to the higher cost of measuring the Levenshtein
distance between long sequences.

@@

\subsection{Seek and construct}
To reduce the size of the search space, we use a dynamic ``seek and construct''
approach whereby queries are processed meanwhile the trie is built. In other
words, each sequence is matched against the trie before it is inserted. To
illustrate why the trie does not need to contain all the sequences upon query,
assume that two sequences A and B are $d$-neighbors. A is processed first. Since
B is not yet inserted, A yields no hit. It is then inserted in the trie. At the
time B is processed, A is a hit for the query and the match A-B is discovered.
This approach guarantees that every hit is discovered, while maintaining the
trie as ``thin'' as possible, thereby reducing the search time.
The whole matching process is summarized in the pseudocode shown in
Algorithms~\ref{alg:starcode} and \ref{alg:poucet}.

@@

\section{Results}
\subsection{Scalability}
\label{scalability}
Write some crap here.

\begin{figure}[!tpb]%figurex
\centerline{\includegraphics[scale=0.47]{scalability.pdf}}
\caption{Scalability. Top left: the running time of starcode is
approximlately $O(n^{1.7})$, where $n$ is the number of sequences to
cluster. Top right: the running time is very sensitive to the maximum
Levenshtein distance used in custering.  Bottom left: the running time
as a function of the length of the sequences has a complex behavior. It
increases initially but then decreases for long sequences because the
lookup search becomes more effective. Bottom right: the scaling of the
relative performance is sub-linear as the number of threads increases.
The algorithm is fully parallel, but the memory bandwidth becomes
limiting on the tested hardware.
}\label{fig:X}
\end{figure}

\subsection{Benchmark against sequence clustering algorithms}
Sequence clustering is routinely used to curate databases of non
redundant nucleotide or protein sequences. We benchmarked starcode
against the two popular sequence clustering algorithms CD-HIT
\citep{pmid23060610} and USEARCH \citep{pmid20709691}.

@@

Using 12 cores, starcode clustered the shuffled 50 million sequences
in 5 minutes and 17 seconds without a single error (the output
consisted of 1 million clusters of size 50).  The running times
of CD-HIT and USEARCH were [59] and [64] minutes respectively, and they
identified 2,362,352 and 2,739,954 clusters respectively. The results
are summarized in Figure~\ref{fig:benchmark}. Both algorithms rely on
heuristics, explaining why the number of clusters is off target. These
results clearly demonstrate that starcode outperforms other clustering
algorithms in speed and accuracy to cluster random sequences.

@@

\begin{figure}[!tpb]
\centerline{\includegraphics{benchmark.pdf}}
\caption{Benchmark of starcode against sequence clustering algorithms
and short read mappers. \textbf{a} Running time compared to CD-HIT and
UCLUST on the dataset described in the text. \textbf{b} Error rate
compared to CD-HIT and UCLUST, expressed as the percentage of clusters
failing to be merged. \textbf{c} Running time compared to Bowtie2, BWA
and GEM on this dataset. The running time is decomposed in extraction
of unique sequences (purple), Burrows-Wheeler indexing (yellow), and
query proper (white). The extraction was performed with the Linux sort
command, so the time is the same in every case. \textbf{d} Error rate
compared to Bowtie2, BWA and GEM, expressed as the proportion of matches
with a single hit. This is an underestimate of the true error rate.}
\label{fig:benchmark}
\end{figure}

@@

For this test, we used the same dataset described above, in which every
sequence has at least 2 distinct matches at a distance 3 (mutant sequences
from the same cluster may be at a distance up to 6 from each other). This
means that we
can use matches with a single hit (themselves) as a lower bound on the inaccuracy.
We used unique sequences to build an index and queried the index with the same
sequences. Figure~\ref{fig:benchmark}c shows the running time of starcode along with the
decomposition of the running time for the three mappers. Note that the time to
extract unique sequences is always the same because we used the Linux
\texttt{sort -u} command in every case. The running time of
starcode is slightly lower than short read mappers when all steps ares
taken into account.  Figure~\ref{fig:benchmark}d shows the lower bound on
the error rate, as estimated by the proportion of single hits. BWA was
found to be the most accurate aligner with a lower bound of 31\% sequences.
with a single match. This measure is an underestimate of the true error
rate, but given that starcode is an exact algorithm, a more accurate
measure is not necessary. In conclusion, starcode can compete with the
short read aligners on the matching problem, and it provides a precision
that none of the other tools can offer.

@@

We set up a test based on the meningitis-causing agent
\textit{Neisseria meningitidis}. The genome of this bacterium is interspersed
with a frequent 12 bp sequence known as DNA uptake sequence \citep{pmid10673000}. We
extracted the 12-mers from both orientations of  the 2.19 Mb genome, yielding
4.39 million 12-mers, consisting of 2.77 million unique sequences. Clustering
the 12-mers with starcode within a Levenshtein distance of 2 took less
than 45 seconds with 12 cores. We identified the known DNA uptake sequence of
\textit{Neisseria meningitidis} (ATGCCGTCTGAA) as the most abundant 12-mer.
This result testifies to the fact that starcode can be used to identify biologically
relevant motifs in bacterial genomes.

To test starcode on another application, we used the RNA-protein
interaction data produced by RNAcompete \citep{pmid19561594}. The mammalian
splicing factor SRSF1 is known to bind RNA GA-rich motifs, but there is
some disagreement about the motif that it recognizes \citep{pmid23562324}.
For each replicate, we replaced the RNAcompete signals by their rank and
extracted the 10-mers from the microarray probes. The 10-mers were given
a score equal to the rank of the probe they belong, and enriched motifs
were found using the sphere clustering of starcode with max Levenshtein
distance 2. The score of the most enriched 10-mer is thus the sum of the
ranks of all 10-mers within this distance. Clustering the 6.3 million
extracted 10-mers with 12 cores took about 20 seconds for each replicate.
The most enriched 10-mers were AGGACACGGA, AGGACACGGA, AGGACGGAGG,
AGGACGGAGG, AGGACACGGA and AGGATACAGG. Except for the last replicate, the
motifs consist of AGGAC and GGA, with a spacer of variable length. This
suggests that the binding of SRSF1 to RNA is flexible, which explains the
poor agreement between the motifs derived from 6-mers or 7-mers.

@@

The speed of starcode also makes it proficient at more general clustering
problems, such as identifying enriched k-mers in genomes and in experimental
data. Here we have given two examples of such applications. In the first, we
recover a known enriched 12-mer in the genome of \textit{Neisseria meningitidis}.
